Copies/mL

### 2023-02-02 code/processing_code/copies_calculator.qmd
Final edits to project_README.md

---
title: "Copies/mL"
format:
  html:
    theme: default
---
Libraries
```{r}
library(tidyverse)
library(here)
```

@@

```{r}
copies_final<- full_join(monthly_final,daily_final)
```

>>>>

---
title: "Copies/mL"
format:
  html:
    theme: default
---
*This script takes Cq value outputs from the CFX and computes it to copies of gene targets of Vibrio*

Libraries
```{r}
library(tidyverse)
library(here)
```

@@

```{r}
copies_final<- full_join(monthly_final,daily_final)
summary(copies_final)
str(copies_final)
```
